---
title: "Weight of Fish"
author: "Wilhelmus Elersich"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
Fish <- read.csv("Fish.csv")
```

# Predicting Fish Weight


## Perch

```{r}
Perch <- filter(Fish, Species == "Perch") %>%
  select(-Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model



The best model is the Two Regressor model that predicts Weight by Height and Width, which gives the highest adjusted R-sqaured value.

```{R}
PerchModel <- lm(Weight~Height + Width, data = Perch)
summary.lm(PerchModel)
```
The adjusted r-squared value is 0.94. The residual standard error is 85.17.

```{R}
PerchModel1 <- lm(Weight~Height + Width + Length2, data = Perch)
summary.lm(PerchModel1)
```

The adjusted R-sqaured value is 0.939. The Residual standard error is 85.87.

These two models, PerchModel and PerchModel1, confirm, through the residual standard errors and Adjusted R-squared values confirm that the above two regressor model is superior to the three regressor model.

## Bream

```{r}
Bream <- filter(Fish, Species == "Bream") %>%
  select(-Species)
```

### Best Models


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The three regressor model, which predicts Weight by Height, Width, and Length1 is the best model, because it has the highest adjusted r-squared value. The best two regressor model predicts based on Length2 and Height.

### Best Two regressor model


```{R}
BreamModel <- lm(Weight~Height + Width + Length1, data = Bream)
summary.lm(BreamModel)
```
The adjusted r-squared value is 0.9372. The residual standard error is 52.43.

```{R}
BreamModel1 <- lm(Weight~Height + Length2, data = Bream)
summary.lm(BreamModel1)
```
The adjusted R-squared value is 0.9356. The Residual standard error is 53.1.

## Roach

```{r}
Roach <- filter(Fish, Species == "Roach") %>%
  select(-Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

By looking at the adjusted R-squared value, we can conclude that the best model is the two regression model, which predicts based off Length3 and Width.


### Best Two regressor model


```{R}
RoachModel <- lm(Weight~Length3 + Width, data = Roach)
summary.lm(RoachModel)
```

The adjusted R-squared value is 0.0.8482. The Residual standard error is 34.61.

## Final Summary Statements

Using leaps, multiple linear regression is much easier. By doing so, we determined the best models for predicting the weight of three types of fish: bream, perch, roach. We also used linear models to confirm the accuracy of our regression.

